---
title: "The plothistory package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The plothistory package}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## How can I used it?

The `plothistory` package enables one to store all plus generated
during a session in a user-defined directory, alike all commands
stored in the `.Rhistory` file. These directories can be reused across
different sessions to keep storing plots.

```{r setup}
library(plothistory)
```

Three directories can be used:

- Temporary directory, as created by `tempdir()`, using the
  `phist_tmp_dir()` function. This temporary directory is deleted once
  the R session closes.
  
```{r}
phist_tmp_dir()
```

- A central cache, using the `phist_cache_dir()` function. 

```{r}
phist_cache_dir()
```

- An arbitrary user-defined directory, using the `phist_dir()`.

```{r}
phist_dir(getwd())
```

In each case, the function will first check if the directory exists,
and create if otherwise. The user will be asked to confirm whether the
central cache directory should be created the first time
`phist_cache_dir()` is used.

The storage of all plots is initiated by the `plothistory()`
function. By default, it will use a temporary directory, but the above
functions can be functions can be passed to `plothistory()` to change
this behaviour.

```{r}
plothistory()
```

The plots are generated using the
[httpgd](https://nx10.github.io/httpgd/) graphics device and can seen
at the URL shown above.

## How does it work?

## Session information

```{r}
sessionInfo()
```
